---
output: 
  html_document:
    self_contained: no
---

``` {r include = FALSE}
library("knitr")
source("dataProcessing.R")
source("graphic1.R")
source("graphic2.R")
source("graph3.R")

```

<center>

# **Twitter and the NBA**
## Not Lame Final INFO 201 Project

***

</br>

### Can the level of engagement with players' Twitter accounts predict their team's audience turnout?

``` {r results = 'asis', echo = FALSE}
createGraphic1()
```

##### The team with the highest average audience turnout was the `r highest_audience$Team` while the team with the lowest average audience turnout was the `r lowest_audience$Team`. The `r highest_retweets$Team` had the highest median number of retweets on Twitter while the `r lowest_retweets$Team` had the lowest median number of retweets on Twitter. However, the `r highest_favorites$Team` had the highest median number of favorites on Twitter while the `r lowest_favorites$Team` had the lowest median number of favorites on Twitter.

</br>

***

</br>

### Do players who perform better on offense or defense experience more engagement with their Twitter accounts?


``` {r results = 'asis', echo = FALSE}
createGraphic2()
```

##### Players with a better offensive rating than defensive rating had greater numbers of both retweets and favorites on Twitter. This suggests that fans are more engaged on social media with players who perform better on offense.

</br>

***

</br>

### Does a player's number of Twitter followers show a stronger correlation with their age or salary?


``` {r results = 'asis', echo = FALSE}
createGraphic3()
```

</center>