---
output: 
  html_document:
    self_contained: no
    toc: true
    toc_depth: 2
    toc_float: true
---

``` {r include = FALSE}
library("knitr")
source("dataProcessing.R")
source("graphic1.R")
source("graphic2.R")
source("graphic3.R")

```

<center>

# **Twitter and the NBA**
### Not Lame INFO 201 Final Project

***

## Summary

Our [repository](https://github.com/lrhabner/Not-Lame-Final-Project) can be accessed on GitHub. 

Our group worked with a dataset entitled [Social Power NBA](https://www.kaggle.com/noahgift/social-power-nba), which we accessed through Kaggle. It is a collection of static .csv files, each of which has information pertaining to teams' audience turnout, players' game statistics, players' off-court characteristics, or players' Twitter statistics. The data was gathered by Noah Gift, who sourced it from ESPN, Basketball-Reference, Twitter, Five-ThirtyEight, and Wikipedia.  

While analyzing this dataset, we considered NBA players to be our target audience. We intended to provide them with insight about the effects of their social media engagement on their basketball games. In addition, we aimed to describe correlations between their statistics, characteristics, and social media engagement. Ultimately, we hope that our discoveries will be impactful to the industry, especially in supporting the "More Than an Athlete" movement.

***

## The Team

### Dawn Thompson
Dawn is a sophomore at the University of Washington intending to major in Informatics and Geography. She has been playing basketball for 12 years and is an active member in the UW intramural leagues. Her favorite NBA team is the Washington Wizards and her favorite player is Kelly Oubre Jr.  

### Jeffrey Wang
Jeff is a sophomore at the University of Washington who is interested in CS and UX design. He has been playing basketball recreatively for 9 years. He is from the bay area where basketball has been booming because of the Golden State Warriors' recent success. However, his favorite player to watch is Kyrie Irving because he got that sauce.

### Logan Habner

### Mark Wu
Mark is a sophomore at the University of Washington who intends to major in ACMS and Informatics. He has been playing basketball for 10 years. His favorite player is Lebron James and supports any team he is on. There is no reason needed to support the GOAT.

***

## Question 1

### Can the level of engagement with players' Twitter accounts and/or the structure of the team predict their audience turnout?

``` {r results = 'asis', echo = FALSE}
createGraphic1()
```

#### About the Graph

The data comes from individual players' social statistics but is grouped by team.  
The **size** of the bubble is based on the **average audience attendance**.  
The **hue** of the bubble is based on the **number of players** on the team.  
Users can view specific statistics by hovering the cursor over the bubble.
Users can zoom in by clicking and dragging to select an area of interest.
Users can reset the view by right-clicking.

</br>

#### Observations

Teams with **less favorites than retweets** saw **lower audience attendance**.  
Teams with **over 20 favorites** saw **higher audience attendance**.  
Teams with **over 15 retweets** saw **higher audience attendance**.  
Teams with **14 to 16 players** had the **highest audience attendance**.  
Teams with **16 to 19 players** had the **average audience attendance**.  
Teams with **12 to 14 players** had the **lowest audience attendance**.

***

## Question 2 

### Do players who perform better on offense or defense experience more engagement with their Twitter accounts?


``` {r results = 'asis', echo = FALSE}
createGraphic2()
```

#### **About the Graph**

The data related to _social media_ comes from individual players' _social statistics_.  
The data related to _players' performances_ comes from players' _seasonal statistics_.

</br>

#### **Observations**

Players with a better **offensive rating** than defensive rating had greater numbers of 
both **retweets** and **favorites** on Twitter. 
This suggests that fans are more engaged on social media with players who **perform better on offense**.

***

## Question 3

### Does a player's number of Twitter followers show a stronger correlation with their age or salary?


``` {r results = 'asis', echo = FALSE}
createGraphic3()
```

</center>