---
output: 
  html_document:
    self_contained: no
---

``` {r include = FALSE}
library("knitr")
library("shiny")
source("graphic1.R")
#source("graphic2.R")
source("graph3.R")

```

<center>

# **Twitter and the NBA**
## Not Lame Final INFO 201 Project

</br>
</br>

### Can the level of engagement with players' Twitter accounts predict their team's audience turnout?

``` {r results = 'asis', echo = FALSE}
createGraphic1()
```

##### In 2017, the team with the highest average audience turnout was the `r highest_audience$Team` while the team with the lowest average audience turnout was the `r lowest_audience$Team`. The `r highest_retweets$Team` had the highest median number of retweets on Twitter while the `r lowest_retweets$Team` had the lowest median number of retweets on Twitter. However, the `r highest_favorites$Team` had the highest median number of favorites on Twitter while the `r lowest_favorites$Team` had the lowest median number of favorites on Twitter.


### Do players who perform better on offense or defense experience more engagement with their Twitter accounts?


``` {r echo = FALSE}
#createGraphic2()
```


### Does a player's number of Twitter followers show a stronger correlation with their age or salary?


``` {r results = 'asis', echo = FALSE}
createGraphic3()
```

</center>